---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nationallakes

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Explore U.S. EPA [National Lakes Assessment (NLA)](https://www.epa.gov/national-aquatic-resource-surveys/nla) data in an R (and people) friendly format. **I'm still adding indicators so check back later for the complete data!**

Some notable differences from the raw data: 

* snake_case column names with some name changes for clarity.
* Available years are combined into a single data frame. If a variable is missing for a year, it is noted by `Not included in {Year}` rather than with `NA`

If you're after the *raw* date, check out the [narsscrapr](https://github.com/corysauve/narsscrapr) package.
 
## Basic Usage 

nationallakes contains survey data organized by *Indicator* and `survey_year`. Available survey years include 2007, 2012, and 2017. However, not all indicators were collected in every survey and only partial results are currently available for 2017.

Available indicators include:
```{r echo=FALSE}
data <- data(package = "nationallakes")$result[, "Item"]
unname(data)
```

All indicator data are available when nationallakes is loaded. To access a particular dataset, simply access it via it's name:
```{r}
library(nationallakes)

dplyr::glimpse(algal_toxins$`2017`)
```

## Installation

You can install the development version of nationallakes from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("corysauve/nationallakes")
```

## Contributing 

I welcome any contributions or suggestions for improving this package! Please open an issue to do so. 

## License 

The nationallakes package is licensed under the MIT License. Please see the [LICENSE](LICENSE.md) for more details.

## Acknowledgments 

The National Lakes Assessment Data (2007, 2012, 2017) data were a result of the collective efforts of dedicated field crews, laboratory staff, data management and quality control staff, analysts and many others from EPA, states, tribes, federal agencies, universities, and other organizations. Please contact nars-hq@epa.gov with any questions.
